---
title: "Conditionals Loops"
author: "Halina Do-Linh"
date: "8/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Task 1
```{r}
pm2_5 <- 200

if (pm2_5 < 100) {
  print("Low to moderate risk")
} else if (pm2_5 <= 100 & pm2_5 < 150) {
  print("Unhealthy for sensitive groups")
} else if (pm2_5 >= 150) {
  print("Health risk present")
}

# my error here was that I did not use the "else if" in the second condition, only used "else". Try to recall what this error message means

```

## Task 2
```{r}
species <- "blue_whale"

if (str_detect(species, "whale")) {
  print("Whales are the best")
}

# changed blue_whale to blue_bird and my output was nothing, yay!

```

## Task 3 
```{r}
max_airtemp_c <- 27

if (max_airtemp_c > 27) {
  print("Temperature too high")
} else if (max_airtemp_c <= 27) {
  print("Temperature OK")
}

# changed air temp from 24.1 to 50 and it worked, yay!

```

## Task 4 

```{r}
base_burrito <- 6.50
main_ingredient <- "chicken"

if (str_detect(main_ingredient, "veggie")) {
  print(base_burrito)
} else if (str_detect(main_ingredient, "chicken")) {
  print(base_burrito + 3)
} else if (str_detect(main_ingredient, "steak")) {
  print(base_burrito + 3.25)
}

```
## Task 5
Create a new vector called fish that contains the values 8, 10, 12, 23 representing counts of different fish types in a fish tank (goldfish, tetras, guppies, and mollies, respectively). Write a for loop that iterates through fish, and returns what proportion of total fish in the tank are that species. Assume that these counts represent all fish in the tank.
```{r}
fish_name <- c("goldfish", "tetras", "guppies", "mollies")
fish <- c(8, 10, 12, 23)
sum_fish <- sum(fish)
sum_fish

# proportion is count of each fish type / 53

proportion_fish <- vector(mode = "numeric", length = length(fish))

for (i in seq_along(fish)) {
  proportion_val <- (fish[i] / sum_fish)
  proportion_fish[i] <- paste(proportion_val, fish_name[i])
}

proportion_fish

```

## Task 6 
There is an existing vector in R called month.name that contains all month names (just try running month.name in the Console to check it out). Write a for loop that iterates over all months in month.name and prints “January is month 1,” “February is month 2”, etc.

Hint: you can index values in the month.name vector just like you would any other vector (e.g., try running month.name[5]).

```{r}
for (i in seq_along(month.name)) {
  print(paste(month.name[i], "is month", i))
}

```



